Papers

### 2024-10-18 papers.qmd
update

-    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2024). [The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research, e1997. <https://doi.org/10.1002/mpr.1997> - [[preprint](https://psyarxiv.com/sakn9)]

@@

@@

>>>>

@@

-   Karadzhov, G., Stafford, T., and Vlachos, A. (2023). [DeliData: A dataset for deliberation in multi-party problem solving](https://dl.acm.org/doi/10.1145/3610056). Proceedings of the ACM on Human-Computer Interaction, CSCW. <https://doi.org/10.1145/3610056> [[arXiv](https://arxiv.org/abs/2108.05271)]

@@

-   Dommett, K., Mensah, S. A., Zhu, J., & Stafford, T. (2024). [Understanding the communicative strategies used in online political advertising and how the public views them](https://doi.org/10.1177/13691481241287177). The British Journal of Politics and International Relations, 0(0). https://doi.org/10.1177/13691481241287177
